MSDS6372Project1

### 2021-01-21 MSDS6372Project1.Rmd
fixing variable column names

#Market.Category: Crossover,Diesel,Exotic,Luxury,High-Performance,Factory Tuner,Performance,Flex Fuel,Hatchback,Hybrid,N/A (Note: Performance column will be handled individually becuase of presence of High-Performance)
marketCat = c("Crossover","Diesel","Exotic","Luxury","High-Performance","Factory Tuner","Flex Fuel","Hatchback","Hybrid","N/A")
marketCat = data.frame(marketCat)
str = "Hatchback,Factory Tuner,High-Performance,N/A";
grepl(marketCat[11,1],str)

@@

CarData %>% select(Market.Category,Performance,'High-Performance','Flex Fuel')
# Check the reading - can later be deleted
head(CarData)
str(CarData)
dim(CarData)
# Convert factor variables
variables.to.factor = c("Make","Model","Engine.Fuel.Type","Transmission.Type","Driven_Wheels","Market.Category","Vehicle.Size","Vehicle.Style","Crossover","Diesel","Exotic","Luxury","High-Performance","Factory Tuner","Performance","Flex Fuel","Hatchback","Hybrid","N/A")
CarData[variables.to.factor] = lapply(CarData[variables.to.factor],factor)
# Look at summary of data
summary(CarData)
summary(CarData$Market.Category)

>>>>

#Market.Category: Crossover,Diesel,Exotic,Luxury,High-Performance,Factory Tuner,Performance,Flex Fuel,Hatchback,Hybrid,N/A (Note: Performance column will be handled individually becuase of presence of High-Performance)
marketCat = c("Crossover","Diesel","Exotic","Luxury","High-Performance","Factory Tuner","Flex Fuel","Hatchback","Hybrid","N/A")
marketCat = data.frame(marketCat)

@@

CarData %>% select(Market.Category,Performance,'High-Performance','Flex Fuel')

# Convert factor variables
variables.to.factor = c("Make","Model","Engine.Fuel.Type","Transmission.Type","Driven_Wheels","Market.Category","Vehicle.Size","Vehicle.Style","Crossover","Diesel","Exotic","Luxury","High-Performance","Factory Tuner","Performance","Flex Fuel","Hatchback","Hybrid","N/A")
CarData[variables.to.factor] = lapply(CarData[variables.to.factor],factor)

# Adjust column names - get ride of - and space in the column names to make analysis easier
# Also make column names more uniform
CarData = CarData %>%
  rename(
    EngineFuelType = Engine.Fuel.Type,
    EngineHP = Engine.HP,
    EngineCylinders = Engine.Cylinders,
    TransmissionType = Transmission.Type,
    DrivenWheels = Driven_Wheels,
    NumberOfDoors = Number.of.Doors,
    MarketCategory = Market.Category,
    VehicleSize = Vehicle.Size,
    VehicleStyle = Vehicle.Style,
    HighwayMPG = highway.MPG,
    CityMPG = city.mpg,
    HighPerformance = `High-Performance`,
    FactoryTuner = `Factory Tuner`,
    FlexFuel = `Flex Fuel`,
    N_A = `N/A`
  )

# Look at summary of data
summary(CarData)
